\section{Strategy Meeting - Project Updates}
\timestamp{Luke Gagnon, Leigh Goetsch}{[10/08/2024]}
\attendees{Peter Wolfgramm, Andrew Needham, Miles Trompeter, Landon Van Mersbergen}

\subsection{Meeting Goals}
\begin{itemize}
    \item Review progress on current project objectives
    \item Discuss next steps for each project area
    \item Identify any roadblocks or challenges
    \item Plan for future strategy meetings
\end{itemize}

\subsection{Project Updates}
The following is a summary of the progress made in each project area and the next steps planned for each group:

\subsubsection{Leblib Path Planning}
\textbf{Group:} Andrew, Peter, Salvin\\
\textbf{Objective:} Set up the Leblib path planning library and begin integrating it with autonomous navigation and odometry.\\
\textbf{Plan:}
\begin{itemize}
    \item Successfully set up the path planning library on the development environment.
    \item Initial testing was not conducted yet; plan to test integration with the robot's autonomous systems and odometry tomorrow.
\end{itemize}
\textbf{Next Steps:}
\begin{itemize}
    \item Tomorrow, test the library with the robot's autonomous functionalities and odometry data.
    \item Identify any adjustments or customizations needed for better integration.
\end{itemize}

\subsubsection{Robot Communication}
\textbf{Group:} Luke, Leigh, Miles\\
\textbf{Objective:} Establish a communication protocol between robots and test message reception.\\
\textbf{Plan:}
\begin{itemize}
  \item Set up a basic test environment to verify correct message reception between robots.
  \item Began discussing the communication protocol for inter-robot messaging, focusing on what specific data needs to be shared.
\end{itemize}
\textbf{Key Considerations for Communication Protocol:}
\begin{itemize}
  \item Location data: Essential for coordinating movements between robots.
  \item Object detection data: Could be useful in determining shared understanding of obstacles or objectives.
  \item Game state: Related to object detection, the state of the game (such as target detection or task progress) may need to be shared.
  \item Help signal: To allow one robot to request assistance from another if necessary.
\end{itemize}
\textbf{Next Steps:}
\begin{itemize}
  \item Finalize the communication protocol, specifying the exact data types to be transmitted.
  \item Implement and test the protocol between the robots.
\end{itemize}

\subsubsection{Task Abstraction}
\textbf{Group:} Not assigned yet\\
\textbf{Objective:} Develop a task management system for handling asynchronous tasks during autonomous robot operation.\\
\textbf{Plan:}
\begin{itemize}
  \item Research two potential approaches: creating a custom task system vs. leveraging the PROS library's task management system.
  \item Determine how events can be triggered within the system to better manage robot actions.
\end{itemize}
\textbf{Next Steps:}
\begin{itemize}
  \item Research both options: creating a custom task system vs. leveraging PROS.
  \item Determine how events can be triggered within the system to better manage robot actions.
\end{itemize}

\subsubsection{Web Dashboard}
\textbf{Status:} Paused / Peripheral\\
\textbf{Objective:} Update and integrate the internal path planning interface to export JSON data.\\
\textbf{Plan:}
\begin{itemize}
  \item The web dashboard interface, developed a few years ago, needs updates to ensure compatibility with our current system.
  \item Initial review of legacy code has not yet been conducted.
\end{itemize}
\textbf{Next Steps:}
\begin{itemize}
  \item Review the legacy code to assess the current implementation.
  \item Ensure the dashboard can export JSON data for use in other areas of the project.
\end{itemize}

\subsubsection{Website Maintenance}
\textbf{Group:} Salvin, Andy\\
\textbf{Objective:} Modernize the website and update the content.\\
\textbf{Plan:}
\begin{itemize}
  \item The website is outdated and has dependency issues with npm, preventing updates in its current state.
  \item Initial steps will involve resolving these dependency issues to make the site functional in modern environments.

\end{itemize}
\textbf{Content Updates Considered:}
\begin{itemize}
  \item Sponsor list.
  \item Links to relevant GitHub repositories (pneumatic reverse engineering, senior design projects, web dashboard, website).
  \item Past engineering notebooks, Onshape designs (past robots), and updated tournament statistics.
  \item Contact information update.
\end{itemize}
\textbf{Next Steps:}
\begin{itemize}
  \item Fix the dependency issues.
  \item Begin content updates as discussed, starting with sponsor lists and repository links.
\end{itemize}
