\section{Tuesday Strategy Meeting}
\timestamp{Luke Gagnon, Leigh Goetsch}{[10/22/2024]}
\attendees{Peter Wolfgramm, Andrew Needham, Miles Trompeter}

\subsection{Meeting Goals}
\begin{itemize}
    \item Try to figure out the reason behind VEXlink issues
    \item VEXlink documentation reading
    \item Get VEX AI team members GHOST project setup and running
\end{itemize}

\subsection{Discussion}
\begin{itemize}
    \item VEXlink Docs: https://drive.google.com/file/d/13mTA6BT7CPskJzh4YgsfAfoH9OgK75Hn/view?pli=1
    \item Excerpts:
    \begin{itemize}
        \item When multiple radios are connected to a V5 brain, the radio in the highest numbered smart port will be used for the controller VEXnet connection, to avoid errors
        \item Data Rate:
        \begin{itemize}
            \item Maximum data rate for manager to worker robot is 1040 bytes/second.
            \item Maximum data rate for worker to manager robot is 520 bytes/second.
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Results}
\begin{itemize}
    \item VEXlink issues are likely due to the order of the controller and the VEXlink device ports
\end{itemize}

\subsection{Action Items}
\textbf{VEXU Team Tasks}
\begin{itemize}
  \item VEXlink\\
  \textbf{Leigh, Miles}
  \item LebLib\\
  \textbf{Andrew}
\end{itemize}

\textbf{VEX AI Team Tasks}
\begin{itemize}
  \item Nano -> V5 microcontroller communication:
  \begin{itemize}
      \item How is the nano and the V5 microcontroller working together?
      \item What is being processed on what?
      \item Create a simple program to send a message from one to the other
  \end{itemize}
  \item ROS2 serial robot messaging
  \begin{itemize}
      \item How is ROS architected?
      \item How is this useful in our use-case?
      \item Write a publisher and subscriber script (or run the one in GHOST's example)
  \end{itemize}
  \item robot -> robot messaging (VEXlink)
  \begin{itemize}
      \item What messages should robots send each other
      \item What message protocol do robotic systems usually use?
      \item What message protocol should we use?
      \item Use VEXlink PROs API to write a simple program to send a message from one robot to another.
  \end{itemize}
  \item Simulation - GHOST\\
  \textbf{Evan, Salvin, Leigh}
  \begin{itemize}
      \item The sim software that GHOST uses is called Gazebo Sim
      \item The python that the bash file ./scripts/launch\_sim.sh runs can be found at 04\_Sim/ghost\_sim/launch/start\_sim.launch.py
      \item There is a typo that causes the world to not load in the sim env, will post the fix later tonight.
      \item What information can the sim env store?
      \item What is the filetype of the world and the model files?
  \end{itemize}
  \item Path planning - GHOST
  \begin{itemize}
      \item GHOST uses https://web.casadi.org/ for path planning
      \item What does this library do?
      \item What are the input and outputs for their algorithm?
  \end{itemize}
  \item MSOE Senior Design - Adversarial Strategy VEX Robot Program
  \begin{itemize}
      \item This is a senior design project from two years ago using RL 
      \item If you are itching for more project setup, load up this project
      \item How does this project represent a robot?
      \item What information does the robot store?
      \item How does the robot choose actions?
  \end{itemize}
\end{itemize}
\textbf{Specific People:}
\begin{itemize}
  \item Nano Setup\\
  \textbf{Evan, Salvin}
  \begin{itemize}
    \item Try following the instructions in this repo to setup your nano and run the example code
  \end{itemize}
  \item Rosie Newbie\\
  \textbf{Andrew}
  \begin{itemize}
    \item Go to the AI Club Learning Tree and follow the instructions to practice requesting rosie and running jobs
    \item I will have some files for you in the next couple days for this
  \end{itemize}
\end{itemize}
